\documentclass[format=acmsmall,review,authorversion,timestamp]{acmart}

%\documentclass[aps,pre,twocolumn,showpacs,preprintnumbers,amsmath,amssymb]{revtex4-1}
%\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb]{revtex4}


\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math


\PassOptionsToPackage{dvipsnames}{xcolor}


\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbold}
%\usepackage[dvipsnames]{xcolor}
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{longtable}
%\usepackage[dvips]{graphicx}
\usepackage{xspace}
\usepackage{bbm}
\usepackage[all]{xy}
%\usepackage{slashbox}
%\usepackage[justification=centering]{caption}
\providecommand{\begeq}[1]{\begin{equation}#1\end{equation}}
\DeclareMathOperator{\tr}{tr}
\providecommand{\norm}[1]{\lVert#1\rVert}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{defi}{Definition}
\newtheorem{rem}{Remark}
\newtheorem{conj}{Conjecture}
\newtheorem{prop}{Proposition}
\DeclareMathOperator{\con}{cond}
\DeclareMathOperator{\diag}{diag}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\newcommand{\michael}[1]{\textcolor{MidnightBlue}{#1}}

%Try to avoid widows and orphans
%\usepackage[all]{nowidow}
\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000



\begin{document}

\acmJournal{TOMS}

% TODO update after acceptance
\acmVolume{99}
\acmNumber{88}
\acmArticle{77}
\acmYear{20XX}
\acmMonth{6}

\citestyle{acmauthoryear}

% TODO
\keywords{}

% TODO
% CCScodes ....



% abstract must preced title in acmart style
\begin{abstract}
In scientific computing, the acceleration of atomistic computer simulations by means of custom hardware is finding ever growing application.
%Accelerating atomistic computer simulations using hardware acceleration is finding ever growing application in scientific computing.
A major limitation, however, is that the high efficiency in terms of performance and low power consumption entails the massive usage of low-precision computing units. Here, based on the approximate computing paradigm, we present an algorithmic method to rigorously compensate for numerical inaccuracies due to low-accuracy arithmetic operations, yet still obtaining exact expectation values using a properly modified Langevin-type equation. %By this, we lay the foundation for the development of efficient MD accelerators.
\end{abstract}



\title{Accurate Sampling with Noisy Forces from Approximate Computing}

\author{Varadarajan Rengaraj}
%\orcid{}
\affiliation{Dynamics of Condensed Matter and Department of Computer Science, Paderborn University, Warburger Str. 100, D-33098 Paderborn, Germany}
\email{rengaraj@campus.uni-paderborn.de}

\author{Michael Lass}
%\orcid{}
\affiliation{Department of Computer Science Paderborn University, Warburger Str. 100, D-33098 Paderborn, Germany}
\affiliation{Paderborn Center for Parallel Computing, Paderborn University, Warburger Str. 100, D-33098 Paderborn, Germany}
\email{michael.lass@uni-paderborn.de}

\author{Christian Plessl}
\orcid{0000-0001-5728-9982}
\affiliation{Department of Computer Science Paderborn University, Warburger Str. 100, D-33098 Paderborn, Germany}
\affiliation{Paderborn Center for Parallel Computing, Paderborn University, Warburger Str. 100, D-33098 Paderborn, Germany}
\email{christian.plessl@uni-paderborn.de}

\author{Thomas D. K\"uhne}
%\orcid{}
\affiliation{Dynamics of Condensed Matter and Center for Sustainable Systems Design, Chair of Theoretical Chemistry, University of Paderborn, Warburger Str. 100, D-33098 Paderborn, Germany}
\email{tdkuehne@mail.upb.de}


%\date{\today}% It is always \today

             %\preprint{APS/123-QED}


%A Valid PACS numbers may be entered using the \verb+\pacs{#1}+ command.
%\pacs{31.15.-p, 31.15.Ew, 71.15.-m, 71.15.Pd}% PACS, the Physics and Astronomy
                             % Classification Scheme.
\maketitle



\section{Introduction}
\input{sections/introduction}

\section{Approximate Computing}
\input{sections/foundations-compsci}
%\input{sections/foundations-chem}

\section{Methodology}
\input{sections/methodology}

\section{Computational details}
\input{sections/compdetails}

\section{Results and Discussion}
\input{sections/results}

\section{Summary}
\input{sections/summary}


% TODO write grant sponsors.. with special environment, see acmart.pdf page 23
%\begin{acks}
%  The authors would like to thank Dr. Yuhua Li for providing the
%  matlab code of the \textit{BEPS} method.
%  The authors would also like to thank the anonymous referees for
%  their valuable comments and helpful suggestions. This work is
%  supported by the \grantsponsor{GS501100001809}{National Natural
%  Science Foundation of
%  China}{https://doi.org/10.13039/501100001809} under Grant
%  No.: ̃\grantnum{GS501100001809}{61273304}
%  and ̃\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
%  Scientists’ Support Program}.
%\end{acks}

\begin{acks}
The authors would like to thank the Paderborn Center for Parallel Computing (PC2) for computing time on OCuLUS and FPGA-based supercomputer NOCTUA. Funding from the Paderborn University's research award for ``Green IT'' is kindly acknowledged. This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 716142).
\end{acks}

% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{report}

\end{document}
